---
title: "Quarto Layout Options"
author: "Mike Gaunt"
format: 
  dashboard:
    embed-resources: true
---

```{r}
library(tidyverse)
library(plotly)
library(reactable)
```

```{r}
plot = plot_ly(data = mtcars, x = ~wt, y = ~qsec, color = ~gear)
table = reactable(mtcars)
```

# Bills

```{r}
plot
```

# Columns Sub Rows {orientation="columns" scrolling="true"}

## Column

```{r}
plot
```

## Column

```{r}
plot
```

```{r}
plot
```

# Columns Sub Rows w/Tab {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column

```{r}
table
```

### Row {.tabset}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}

# Col Sub Rows w/Tab Adj Hght {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column {width="70%"}

### Row {height="30%"}

```{r}
table
```

### Row {.tabset height="70%"}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}

# Columns Sub Rows w/Tab {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column {width="70%"}

### Row {height="30%"}

```{r}
table
```

### Row {.tabset, height=70%}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}
