---
title: "Quarto Layout Template"
author: "Mike Gaunt"
format: 
  dashboard:
    embed-resources: true
---

```{r}
library(tidyverse)
library(plotly)
library(reactable)
library(crosstalk)
```

```{r}
plot = plot_ly(data = mtcars, x = ~wt, y = ~qsec, color = ~gear)
table = reactable(mtcars)
```

```{r}
plot = plot_ly(data = mtcars, x = ~wt, y = ~qsec, color = ~gear)
mtcars_sd = SharedData$new(mtcars
                           ,group = "mtcars_subset")

mtcars_small = SharedData$new(mtcars %>% filter(hp > 160)
                           ,group = "mtcars_subset")

temp_crosstalk = bscols(
  widths = c(6,6)
  ,plot_ly(mtcars_small, x = ~disp, y = ~hp, color = ~vs)
  ,table = reactable(
    mtcars_sd
    ,columns = list(
      vs = colDef(show = FALSE)
      ,am = colDef(show = FALSE)
      ,gear = colDef(show = FALSE)
      ,carb = colDef(show = FALSE)
    ), onClick = "select", selection = "multiple")
)
```

```{r}

shared_df <- SharedData$new(iris)

item = bscols(
  widths = c(5, 5)
  ,ggplotly(ggplot(shared_df) +
      geom_point(aes(x = Sepal.Width, y = Sepal.Length, colour = Species)))
  ,reactable(shared_df
             , onClick = "select", selection = "multiple"))


```

# Bills

```{r}
plot
```

# Columns Sub Rows {orientation="columns" scrolling="true"}

## Column

```{r}
plot
```

## Column

```{r}
#| title: "Research Needs Gap Table"
plot
```

```{r}
plot
```

# Columns Sub Rows w/Tab {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column

```{r}
table
```

### Row {.tabset}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}

# Col Sub Rows w/Tab Adj Hght {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column {width="70%"}

### Row {height="30%"}

```{r}
table
```

### Row {.tabset height="70%"}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}

# Columns Sub Rows w/Tab {orientation="columns" scrolling="false"}

## Column

```{r}
plot
```

## Column {width="70%"}

### Row {height="30%"}

```{r}
table
```

### Row {.tabset, height=70%}

#### Header 1

```{r}
plot
```

#### Header 2

```{r}
table
```

#### Header 3

```{r}
table
```

###  {.unnumbered}
